ISYE 6501

### 2022-10-10 hw5-1/submission.Rmd
hw 7

If we want we can still test if drop the lowest variables: Time and Pop is helpful.

@@

+ Dicharge Disposition : The discharge disposition/location code is an important factor for determining the probability of readmission . People with a relatively high risk score and requiring post acute care when  discharged directly to home are more prone to getting readmitted.

+ Length of Stay : The period/length of stay also has a strong predictive power on the probability of readmission. Both low and high values are correlated with higher readmission rate.Low length of stay can lead to readmission due to patient not being treated properly without proper diagnosis and people with higher length of stay get readmitted due to Hospital acquired diseases.

+ Risk Score : The overall risk score of a patient based on past medical history and demographics is also a good prediction variable for the probability of readmission.

+ Change in medication/procedure during hospitalization : This is also a significant feature related with higher readmission rates. People who have seen greater changes in procedure/prescribed medicine are more prone to getting readmitted.

+ Number of ED/IP visits within the rolling 1 year : This utilization metric is also a good predictor as it encapsulates the overall profile of a patient . Patients with higher ED/IP visits are more prone to getting readmitted within 30 days of being discharged.

>>>>

If we want we can still test if dropping the lowest variables, Time and Pop is helpful. This shall further simplify our model, which is especially helpful with small amount of data.

@@

-   Dicharge Disposition : The discharge disposition/location code is an important factor for determining the probability of readmission . People with a relatively high risk score and requiring post acute care when discharged directly to home are more prone to getting readmitted.

-   Length of Stay : The period/length of stay also has a strong predictive power on the probability of readmission. Both low and high values are correlated with higher readmission rate.Low length of stay can lead to readmission due to patient not being treated properly without proper diagnosis and people with higher length of stay get readmitted due to Hospital acquired diseases.

-   Risk Score : The overall risk score of a patient based on past medical history and demographics is also a good prediction variable for the probability of readmission.

-   Change in medication/procedure during hospitalization : This is also a significant feature related with higher readmission rates. People who have seen greater changes in procedure/prescribed medicine are more prone to getting readmitted.

-   Number of ED/IP visits within the rolling 1 year : This utilization metric is also a good predictor as it encapsulates the overall profile of a patient . Patients with higher ED/IP visits are more prone to getting readmitted within 30 days of being discharged.
